---
name: Simone
surname: D'Ambrogio
position: "PhD"
pronouns: he/him
address: "Experimental Psychology, University of Oxford"
phone: +39 392 0995325
www: simonedambrogio.github.io
email: "simone.dambrogio@psy.ox.ac.uk"
github: simonedambrogio
linkedin: simone-d-ambrogio-abb382178/?locale=en_US
date: "`r format(Sys.time(), '%B %Y')`"
csl: apa-cv.csl
header-includes:
   - \usepackage{longtable}
output: 
  vitae::awesomecv:
    keep_tex: true
    pandoc_args: ["--lua-filter=lua/strong.lua"]
---

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(purrr)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD in Experimental Psychology", "2021 - present", "University of Oxford", "Oxford, UK",
  "Visiting Graduate Scholar, Wharton Neuroscience Initiative", "2020", "University of Pennsylvania", "Philadelphia, Pennsylvania",
  "M.Sc. in Applied Cognitive Psychology (Cum Laude)", "2017-2020", "University of Padua", "Padua, Italy",
  "Erasmus + Program", "2018", "Leiden University", "Leiden, Netherlands",
  "B.Sc. in Psychology (First class Honours)", "2017-2017", "University of Padua", "Padua, Italy",
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Research

\begin{cventries}
    \cventry{\normalfont{Studying how the brain supports adaptive behavior, combining machine learning, non-invasive brain stimulation, and high-resolution brain imaging in humans and non-human primates. }}{\href{https://www.psy.ox.ac.uk/research/decision-and-action-laboratory}{Decision and Action, University of Oxford}}{Oxford, UK}{2021 - present}{}\vspace{-4.0mm}
    \cventry{\normalfont{Analysis and modeling of eye-tracking and pupillometry to study the role of attention in consumer decision-making. }}{\href{https://plattlabs.rocks/}{Platt Lab, Wharton Neuroscience Initiative, UPenn}}{Philadelphia, Pennsylvania}{2020}{}\vspace{-4.0mm}
    \cventry{\normalfont{Analysis and modeling of decision-making.}}{\href{https://jrp.pscholars.org/}{Junior Researcher Programme}}{Cambridge, UK}{2020}{}\vspace{-4.0mm}
    \cventry{\normalfont{Modeling and analyzing decision-making to enhance individual and societal well-being. }}{\href{https://jdmlabpd.dpss.psy.unipd.it/jdmlab/en/}{Judgment and Decision-Making Lab, Padua University}}{Padua, Italy}{2018-2020}{}\vspace{-4.0mm}
    \cventry{\normalfont{Development of statistical methods for data analysis in behavioural science. }}{\href{https://psicostat.dpss.psy.unipd.it/}{PsicoStat Lab, Padua University}}{Padua, Italy}{2017-2020}{}\vspace{-4.0mm}
\end{cventries}

# Conferences

\begin{cventries}
    \cventry{\normalfont{Hybrid artificial neural network modelling predicts behaviour and neural activity in a solution for Buridan's ass.}}{\textbf{Mathematics Of Neuroscience and AI}\normalfont{ (\href{https://www.youtube.com/watch?v=6LEm0jDcuxI&list=PLA59nMLAkDyiyYoISlQDDnMY4pxKmTsBC&index=51}{\faYoutubePlay\, Talk}) }}{Rome, Italy}{2024}{}\vspace{-4.0mm}
    \cventry{\normalfont{Discovery of Cognitive Strategies for Information Sampling with Deep Cognitive Modelling and Investigation of their Neural Basis}}{\textbf{Foraging and information seeking conference}\normalfont{ (\href{https://github.com/simonedambrogio/CV/blob/main/files/post.pdf}{\faFilePdfO\, Poster})}}{Lyon, France}{2024}{}\vspace{-4.0mm}
    \cventry{\normalfont{Visuospatial working memory modulates the influence of
visual attention on binary choice}}{\textbf{Interdisciplinary Symposium on Decision Neuroscience}\normalfont{ (Poster) }}{Online}{2021}{}\vspace{-4.0mm}
    \cventry{\normalfont{The Effect of Celebrity and Visual Attention on Value-Based Decisions}}{\textbf{Society for Neuroeconomics}\normalfont{ (Poster) }}{Online}{2020}{}\vspace{-4.0mm}
    \cventry{\normalfont{The Attentional Drift Diffusion Model with Temporal Information}}{\textbf{Junior Researcher Programme Conference}\normalfont{ (Poster) }}{Siena, Italy}{2019}{}\vspace{-4.0mm}
    \cventry{\normalfont{Estimation of the attentional drift diffusion model parameters via Random Utility}}{\textbf{PsicoStat Meeting}\normalfont{ ( \href{https://simone-dambrogio.shinyapps.io/presentation/}{\faGlobe\, Talk)} }}{Padova, Italy}{2019}{}\vspace{-4.0mm}
\end{cventries}

# Publications

```{r}
bibliography_entries("packages.bib")
```

# Technical skills

```{r techtable, results='markup'}
library(kableExtra)
table_output <- tribble(
   ~`Coding Languages`, ~Software, ~Other,
  "Julia -- R -- Python -- STAN -- Node.js -- JavaScript",
  "FSL -- SPM",
  "Git -- Markdown -- LaTex -- Quarto -- Arduino"
) |>
kable(booktabs = F, align = 'c', escape = F, format = "latex", linesep = "") |>
kable_styling(full_width = F, font_size = 10, 
              latex_options = c("HOLD_position")) |>
row_spec(0, bold = T, color = "#009acd") |>
row_spec(1, bold = F, color = "#7f7f7f") |>
column_spec(column = 1, width = '7.125cm', border_right = F, border_left = F) |>  # 50% of total (14.25cm)
column_spec(column = 2, width = '3.5625cm', border_right = F, border_left = F) |>  # 25% of total
column_spec(column = 3, width = '3.5625cm', border_right = F, border_left = F) |>  # 25% of total
add_header_above(c(" " = 3), line = F)

# Remove hlines
gsub('\\\\hline', '', table_output)
```


