%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\colorlet{awesome}{awesome-red}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Simone}{D'Ambrogio}

\position{PhD}
\address{Experimental Psychology, University of Oxford}

\pronouns{he/him}
\mobile{+39 392 0995325}
\email{\href{mailto:simone.dambrogio@psy.ox.ac.uk}{\nolinkurl{simone.dambrogio@psy.ox.ac.uk}}}
\homepage{simonedambrogio.github.io}
\github{simonedambrogio}
\linkedin{simone-d-ambrogio-abb382178/?locale=en\_US}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


\usepackage{longtable}

% Pandoc CSL macros
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}

\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {January 2025}
    {Simone D'Ambrogio~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\section{Education}\label{education}

\begin{cventries}
    \cventry{PhD in Experimental Psychology}{University of Oxford}{Oxford, UK}{2021-Today}{}\vspace{-4.0mm}
    \cventry{Visiting Graduate Scholar, Wharton Neuroscience Initiative}{University of Pennsylvania}{Philadelphia, Pennsylvania}{2020}{}\vspace{-4.0mm}
    \cventry{M.Sc. in Applied Cognitive Psychology (Cum Laude)}{University of Padua}{Padua, Italy}{2017-2020}{}\vspace{-4.0mm}
    \cventry{Erasmus + Program}{Leiden University}{Leiden, Netherlands}{2018}{}\vspace{-4.0mm}
    \cventry{B.Sc. in Psychology (First class Honours)}{University of Padua}{Padua, Italy}{2017-2017}{}\vspace{-4.0mm}
\end{cventries}

\section{Research}\label{research}

\begin{cventries}
    \cventry{\normalfont{Studying how the brain supports adaptive behavior, combining machine learning, non-invasive brain stimulation, and high-resolution brain imaging in humans and non-human primates. }}{\href{https://www.psy.ox.ac.uk/research/decision-and-action-laboratory}{Decision and Action, University of Oxford}}{Oxford, UK}{2021 - present}{}\vspace{-4.0mm}
    \cventry{\normalfont{Analysis and modeling of eye-tracking and pupillometry to study the role of attention in consumer decision-making. }}{\href{https://plattlabs.rocks/}{Platt Lab, Wharton Neuroscience Initiative, UPenn}}{Philadelphia, Pennsylvania}{2020}{}\vspace{-4.0mm}
    \cventry{\normalfont{Analysis and modeling of decision-making.}}{\href{https://jrp.pscholars.org/}{Junior Researcher Programme}}{Cambridge, UK}{2020}{}\vspace{-4.0mm}
    \cventry{\normalfont{Modeling and analyzing decision-making to enhance individual and societal well-being. }}{\href{https://jdmlabpd.dpss.psy.unipd.it/jdmlab/en/}{Judgment and Decision-Making Lab, Padua University}}{Padua, Italy}{2018-2020}{}\vspace{-4.0mm}
    \cventry{\normalfont{Development of statistical methods for data analysis in behavioural science. }}{\href{https://psicostat.dpss.psy.unipd.it/}{PsicoStat Lab, Padua University}}{Padua, Italy}{2017-2020}{}\vspace{-4.0mm}
\end{cventries}

\section{Conferences}\label{conferences}

\begin{cventries}
    \cventry{\normalfont{Hybrid artificial neural network modelling predicts behaviour and neural activity in a solution for Buridan's ass.}}{\textbf{Mathematics Of Neuroscience and AI}\normalfont{ (\href{https://www.youtube.com/watch?v=6LEm0jDcuxI&list=PLA59nMLAkDyiyYoISlQDDnMY4pxKmTsBC&index=51}{\faYoutube Talk}) }}{Rome, Italy}{2024}{}\vspace{-4.0mm}
    \cventry{\normalfont{Discovery of Cognitive Strategies for Information Sampling with Deep Cognitive Modelling and Investigation of their Neural Basis}}{\textbf{Foraging and information seeking conference}\normalfont{ (\href{"https://github.com/simonedambrogio/CV/blob/main/files/Poster%20Simone%20D'Ambrogio.pdf"}{Poster})}}{Lyon, France}{2024}{}\vspace{-4.0mm}
\end{cventries}

\section{Publications}\label{publications}

\phantomsection\label{refs-c5ea07e26ef96443943e38a4ce333d99}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-kavussanu2025psychological}
1. Kavussanu, M., Rubaltelli, E., Leo, I., Hurst, P., Giovannoni, M.,
Barkoukis, V., Lucidi, F., \textbf{D'Ambrogio, S.,} \& Ring, C. (2025).
A psychological intervention reduces doping likelihood in italian
athletes: A replication and extension. \emph{Psychology of Sport and
Exercise}, \emph{77}, 102761.
\url{https://www.sciencedirect.com/science/article/pii/S1469029224001729}

\bibitem[\citeproctext]{ref-d2023celebrity}
2. \textbf{D'Ambrogio, S.,} Werksman, N., Platt, M. L., \& Johnson, E.
N. (2023). How celebrity status and gaze direction in ads drive visual
attention to shape consumer decisions. \emph{Psychology \& Marketing},
\emph{40}(4), 723--734.
\url{https://onlinelibrary.wiley.com/doi/full/10.1002/mar.21772}

\bibitem[\citeproctext]{ref-priolo2023robustness}
3. Priolo, G., Stablum, F., Vacondio, M., \textbf{D'Ambrogio, S.,}
Caserotti, M., \& others. (2023). \emph{The robustness of mental
accounting: A global perspective}. \url{https://tibble.tidyverse.org/}

\bibitem[\citeproctext]{ref-ruggeri2022globalizability}
4. Ruggeri, K., Panin, A., Vdovic, M., Veckalov, B., Abdul-Salaam, N.,
Achterberg, J., Akil, C., Amatya, J., Amatya, K., \textbf{D'Ambrogio,
S.,} Andersen, T. L., \& others. (2022). The globalizability of temporal
discounting. \emph{Nature Human Behaviour}, \emph{6}(10), 1386--1397.
\url{https://www.nature.com/articles/s41562-022-01392-w}

\end{CSLReferences}



\end{document}
